Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/experiments.tex
fixing improvement values in experimental section text

%\eva{Fix Table 1 caption. It's not the difference, but savings. Difference is absolute.}
%\eva{Compute the actual averages for all F, G, H, K and not only approximations}
For the inverted pendulum, minimal uniform precision saves on average $57.5\%$ of memory
compared to a uniform 32 bit baseline overall, i.e. for F, G, H and K together. 
Mixed-precision further reduces the memory
requirement by $10.4\%$ on average with respect to the minimal uniform baseline. 
\autoref{tab:ipd} shows a more detailed breakdown of the memory requirements and savings
between F and G and H and K.
The memory requirements for the storage of hyperplanes H and K depends only on
the size of the tubes $\varepsilon_Q$ so that memory requirements remain constant
for fixed $\varepsilon_Q$.

%\eva{Compute actual and overall averages here too}
For the aircraft example, minimal uniform precision saves on average $33.5\%$
overall w.r.t. a uniform 32 bit baseline, and mixed-precision saves an
additional $17.6\%$ w.r.t. minimal uniform precision. We observe higher relative
memory savings by mixed-precision for storing H and K than for the inverted pendulum example.

@@

\autoref{tab:di} shows the results of this experiment.
We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $49.8\%$ of memory
compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
Moreover, mixed-precision reduces the memory requirement by an additional
$9.6\%$ on average with respect to the minimal uniform baseline.
We further observe that relative savings remain largely constant for different 
prediction horizons.
% \autoref{tab:di} shows the stability of memory tuning in Daisy is
% constant with respect to the number of controllers or hyperplanes. This is true
% for both F, G and H, K. Indeed, the memory gain from uniform in 32bits and
% minimal uniform (\%32vU) is constant among different input values m. The same
% holds for (\%UvM).

>>>>

%\eva{Fix Table 1 caption. It's not the difference, but savings. Difference is absolute.}
%\eva{Compute the actual averages for all F, G, H, K and not only approximations}
For the inverted pendulum, minimal uniform precision saves on average $52.6\%$ of memory
compared to a uniform 32 bit baseline overall, i.e. for F, G, H and K together. 
Mixed-precision further reduces the memory
requirement by $10.5\%$ on average with respect to the minimal uniform baseline (and 57.5\% w.r.t to 
uniform 32 bit baseline). 
\autoref{tab:ipd} shows a more detailed breakdown of the memory requirements and savings
between F and G and H and K.
The memory requirements for the storage of hyperplanes H and K depends only on
the size of the tubes $\varepsilon_Q$ so that memory requirements remain constant
for fixed $\varepsilon_Q$.

%\eva{Compute actual and overall averages here too}
For the aircraft example, minimal uniform precision saves on average $19.3\%$
overall w.r.t. a uniform 32 bit baseline, and mixed-precision saves an
additional $17.7\%$ w.r.t. minimal uniform precision (33.6\% w.r.t to uniform 32 bit). We observe higher relative
memory savings by mixed-precision for storing H and K than for the inverted pendulum example.

@@

\autoref{tab:di} shows the results of this experiment.
We observe that our analysis scales up to 1829 controllers and 14632 hyperplanes in a few hours.  The computed minimal uniform precision saves on average $44.5\%$ of memory
compared to a uniform $32$ bit baseline overall (for F, G, H and K together). 
Moreover, mixed-precision reduces the memory requirement by an additional
$9.3\%$ on average with respect to the minimal uniform baseline (49.6\% w.r.t. uniform 32 bit).
We further observe that relative savings remain largely constant for different 
prediction horizons.
% \autoref{tab:di} shows the stability of memory tuning in Daisy is
% constant with respect to the number of controllers or hyperplanes. This is true
% for both F, G and H, K. Indeed, the memory gain from uniform in 32bits and
% minimal uniform (\%32vU) is constant among different input values m. The same
% holds for (\%UvM).
